---
title: "pRRophetic or oncoPredict"
author: "Wei"
date: '2023-11-14'
output:
html_document: default
---

# 1. loading library and function
```{r}
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(cowplot))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(ggbeeswarm))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(pRRophetic))
suppressPackageStartupMessages(library(pacman))
pacman::p_load(tidyverse,ggpubr,rstatix,ggsci,ggsignif,reshape2)
options(dplyr.summarise.inform = FALSE)

```

# 2. source function and loading data 
```{r}
# input expr_data
expr_data <- read_rds('/Users/xuewei/ZxProjects/CRC/TCGA/01_Data/TCGA-COAD.tpm_clinical.rds')
expr_data <- expr_data %>% 
  rownames_to_column(var = "Gene_symbol")
expr_data <- as.data.frame(data.table::transpose(expr_data, keep.names = "Gene_symbol", make.names = 1))
expr_data <- expr_data %>% 
  column_to_rownames(var = "Gene_symbol")

# Group
group_type <- read.table("/Users/xuewei/ZxProjects/CRC/2023_GSE231559/01_preprocessing/32_Macrophage_Figures/Rds_02_Lasso_Cox_04_risk_group_surv.txt", sep = "\t", h = T, check.names = F)

```

# 3. Data process
```{r}
data(PANCANCER_IC_Tue_Aug_9_15_28_57_2016)
data(cgp2016ExprRma)

# COAD_drug %>% 
#   select(TCGA.classification) %>% 
#   unique()
COAD_drug <- drugData2016 %>% 
  select(Drug.name, TCGA.classification, Tissue, Tissue.sub.type) %>% 
  filter(TCGA.classification=="COREAD") %>% 
  distinct()

```

# 4. Dabrafenib
# 4.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Dabrafenib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 4.2 join group Dabrafenib
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 4.3 boxplot Dabrafenib
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Dabrafenib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Dabrafenib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 5. Camptothecin
## 5.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Camptothecin",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 5.2 join group Camptothecin
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 5.3 boxplot Camptothecin
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Camptothecin_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Camptothecin')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 6. Docetaxel
## 6.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Docetaxel",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 6.2 join group Docetaxel
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 6.3 boxplot Docetaxel
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Docetaxel_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Docetaxel')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 7. Gefitinib
## 7.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Gefitinib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 7.2 join group Gefitinib
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 7.3 boxplot Gefitinib
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Gefitinib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Gefitinib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 8. Gemcitabine
## 8.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Gemcitabine",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 8.2 join group Gemcitabine
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 8.3 boxplot Gemcitabine
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Gemcitabine_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Gemcitabine')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 9. Pazopanib
## 9.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Pazopanib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 9.2 join group Pazopanib
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 9.3 boxplot Pazopanib
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Pazopanib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Pazopanib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 10. Sunitinib
## 10.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Sunitinib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 10.2 join group Sunitinib
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 10.3 boxplot Sunitinib
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Sunitinib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Sunitinib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 11. 5-Fluorouracil
## 11.1 pRRopheticPredict
```{r}
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="5-Fluorouracil",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

```

## 11.2 join group 5-Fluorouracil
```{r}
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

```

## 11.3 boxplot 5-Fluorouracil
```{r}
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_5-Fluorouracil_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of 5-Fluorouracil')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```


# 12. Erlotinib
```{r}
## 1. pRRopheticPredict
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Erlotinib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

# 2. join group Erlotinib
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

# 3. boxplot Erlotinib
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Erlotinib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Erlotinib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 13. Cetuximab
```{r}
## 1. pRRopheticPredict
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Cetuximab",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

# 2. join group Cetuximab
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

# 3. boxplot Cetuximab
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Cetuximab_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Cetuximab')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 14. Sorafenib
```{r}
## 1. pRRopheticPredict
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Sorafenib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

# 2. join group Sorafenib
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

# 3. boxplot Sorafenib
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Sorafenib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Sorafenib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 15. Crizotinib
```{r}
## 1. pRRopheticPredict
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Crizotinib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

# 2. join group Crizotinib
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

# 3. boxplot Crizotinib
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Crizotinib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Crizotinib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 16. Imatinib
```{r}
## 1. pRRopheticPredict
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Imatinib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

# 2. join group Imatinib
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

# 3. boxplot Imatinib
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Imatinib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Imatinib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

# 17. Tipifarnib
```{r}
## 1. pRRopheticPredict
expr_data <- as.matrix(expr_data)
predictedPtype <- pRRopheticPredict(testMatrix=expr_data,
                                    drug="Tipifarnib",
                                    tissueType = "all",
                                    batchCorrect = "eb",
                                    selection = 1,
                                    dataset = "cgp2016")
predictedPtype <- as.data.frame(predictedPtype) %>% 
  rownames_to_column("Sample")

# 2. join group Tipifarnib
predictedPtype2 <- predictedPtype %>% 
  right_join(group_type, by = c("Sample" = "sample_id")) %>% 
  mutate(Group = ifelse(risk_group == "low_risk", "Low", "High"))

summary(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)
summary(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)
wilcox.test(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype, predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)

# 3. boxplot Tipifarnib
predictedPtype2$Group <- factor(predictedPtype2$Group, levels=c("Low", "High"))

pdf("20231114_Tipifarnib_boxplot_v1.pdf", height=5, width=5)

ggplot(data = predictedPtype2,
       aes(y = predictedPtype,
           x = Group))+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.40, y=median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="Low",]$predictedPtype)), color = "#000000", size = 6)+
  annotate("text", x=2.41, y=median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype), label=sprintf("%0.2f", median(predictedPtype2[predictedPtype2$Group=="High",]$predictedPtype)), color = "#000000", size = 6)+
  geom_boxplot(alpha = 0.8, width=0.5,
               fill = c('#3b9a9c','#ffb549'))+
  theme_bw()+
  ylab('Predicted sensitivity of Tipifarnib')+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))

dev.off()

```

