---
title: "KM of IOBR"
author: "Wei"
date: '2023-11-15'
output:
html_document: default
---

# 1. loading library
```{r}
suppressPackageStartupMessages(library(IOBR))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(tidyHeatmap))
suppressPackageStartupMessages(library(maftools))
suppressPackageStartupMessages(library(ggpubr))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(survival))
suppressMessages(library(writexl))
suppressPackageStartupMessages(library(readxl))
options(dplyr.summarise.inform = FALSE)

```

```{r}
# if (!requireNamespace("BiocManager", quietly = TRUE))
#   install.packages("BiocManager")
# BiocManager::install(version = "3.12")
# 
# BiocManager::install("Cairo", force = TRUE)
# BiocManager::install("ComplexHeatmap", force = TRUE)
# BiocManager::install("tidyHeatmap", force = TRUE)

# # options("repos"= c(CRAN="https://mirrors.tuna.tsinghua.edu.cn/CRAN/"))
# # options(BioC_mirror="http://mirrors.tuna.tsinghua.edu.cn/bioconductor/")
# if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager")
# 
# depens<-c('tibble', 'survival', 'survminer', 'limma', "DESeq2","devtools", 'limSolve', 'GSVA', 'e1071', 'preprocessCore', 
#           "devtools", "tidyHeatmap", "caret", "glmnet", "ppcor",  "timeROC", "pracma", "factoextra", 
#           "FactoMineR", "WGCNA", "patchwork", 'ggplot2', "biomaRt", 'ggpubr', 'ComplexHeatmap')
# for(i in 1:length(depens)){
#   depen<-depens[i]
#   if (!requireNamespace(depen, quietly = TRUE))  BiocManager::install(depen,update = FALSE, force = TRUE)
# }
# 
# if (!requireNamespace("IOBR", quietly = TRUE))
#   devtools::install_github("IOBR/IOBR")

```

# 2. loading data
```{r}
COAD.tpm <- read_rds("/Users/xuewei/ZxProjects/CRC/TCGA/01_Data/TCGA-COAD.tpm_clinical.rds") 
COAD.risk_group <- read.csv("/Users/xuewei/ZxProjects/CRC/2023_GSE231559/01_preprocessing/32_Macrophage_Figures/Rds_02_Lasso_Cox_04_risk_group_surv.txt", sep = "\t", h = T, check.names = F)

```

# 3. lasso cox
## 3.1 prepare input data
```{r}
OS_Sig1 <- COAD.risk_group %>% 
  select(sample_id, time, status, risk_score, risk_group) %>% 
  mutate(Status = ifelse(risk_score >= quantile(COAD.risk_group$risk_score, 0.5), "High", "Low")) %>% 
  rename(OS.status = status, OS = time) %>% 
  distinct()
OS_Sig1 <- na.omit(OS_Sig1)

COAD.group <- OS_Sig1 %>% 
  dplyr::select(sample_id, Status) %>% 
  rename(ID = sample_id,
         group = Status
         )
pset <- COAD.group

```

## 3.2 COAD.tpm
```{r}
COAD.tpm2 <- COAD.tpm %>% 
  rownames_to_column(var="sample")
COAD.tpm3 <- COAD.tpm2 %>% 
  right_join(COAD.group, by = c("sample" = "ID")) %>% 
  dplyr::select(-group)

eset_stad <- as.data.frame(data.table::transpose(COAD.tpm3, keep.names = "Gene_symbol", make.names = 1)) %>%
  column_to_rownames(var="Gene_symbol")

```

# 4. Signature And TME Deconvolution Module
## 4.1 Estimate TME associated signatures-(through ssGSEA method)
```{r}
sig_res<-calculate_sig_score(pdata           = NULL,
                             eset            = eset_stad,
                             signature       = signature_collection,
                             method          = "ssgsea",
                             mini_gene_count = 2)
# join res and group
sig_res_join <- sig_res %>% 
  right_join(pset, by = c("ID" = "ID"))

```

## 4.2 Available Methods to Decode TME Contexture
```{r}
# 解卷积计算tme组分 ----
cibersort <- deconvo_tme(eset = eset_stad, 
                         method = "cibersort", 
                         arrays = FALSE, 
                         perm = 200)

epic <- deconvo_tme(eset = eset_stad,
                    method = "epic",
                    arrays = FALSE)

mcp <- deconvo_tme(eset = eset_stad,
                   method = "mcpcounter")

xcell <- deconvo_tme(eset = eset_stad,
                     method = "xcell",
                     arrays = FALSE)

estimate <- deconvo_tme(eset = eset_stad,
                        method = "estimate")

timer <- deconvo_tme(eset = eset_stad,
                     method = "timer",
                     group_list = rep('COAD', dim(eset_stad)[2]))

quantiseq <- deconvo_tme(eset = eset_stad,
                         tumor = TRUE,
                         arrays = FALSE,
                         scale_mrna = TRUE,
                         method = "quantiseq")

ips <- deconvo_tme(eset = eset_stad,
                   method = "ips",
                   plot= FALSE)

tme_combine <- cibersort %>% 
  inner_join(.,mcp,by       = "ID") %>% 
  inner_join(.,xcell,by     = "ID") %>%
  inner_join(.,epic,by      = "ID") %>% 
  inner_join(.,estimate,by  = "ID") %>% 
  inner_join(.,timer,by     = "ID") %>% 
  inner_join(.,quantiseq,by = "ID") %>% 
  inner_join(.,ips,by       = "ID")

write_xlsx(
  list(ssgsea = sig_res,
       tme_cell = tme_combine
       ), 'immune_IOBR_main.xlsx')

```


# 5. Identify phenotype relevant signatures
## 5.1 Construct phenotype group
```{r}
# 哪些signature与表型相关 -----
sig_res <- read_xlsx('immune_IOBR_main.xlsx', sheet = 1)

pset$group <- factor(pset$group, levels = c('Low', 'High'))

res <- iobr_cor_plot(pdata_group           = pset,
                   id1                   = "ID",
                   feature_data          = sig_res,
                   id2                   = "ID",
                   target                = NULL,
                   group                 = "group",
                   is_target_continuous  = FALSE,
                   padj_cutoff           = 1,
                   index                 = 1,
                   category              = "signature",
                   # signature_group       = sig_group,
                   signature_group       = sig_group[c(1,2,3)],
                   ProjectID             = 'NK',
                   # palette_box           = "paired1",
                   palette_box           = 'paired1',
                   palette_corplot       = "pheatmap",
                   palette_heatmap       = 2,
                   feature_limit         = 26,
                   character_limit       = 30,
                   show_heatmap_col_name = FALSE,
                   show_col              = FALSE,
                   show_plot             = TRUE,
                   path = paste0("1-relevant-signatures"))

```

## 5.2 select relevant signatures
```{r}
# 最相关signature中是哪个基因与表型相关 -----
# pos_sig <- c('CellCycle_Reg', 'CellCycle', 'Mismatch_Repair', 'EMT2', 'Pan_F_TBRs', 'MDSC_Wang_et_al', 'CAF_Peng_et_al', 'TGFb_Family_Member_Li_et_al', 'T_cell_exhaustion_Peng_et_al', 'T_cell_regulatory_Peng_et_al', 'ICB_resistance_Peng_et_al', 'Glycolysis')
pos_sig <- c('Pan_F_TBRs', 'EMT1', 'EMT2', 'EMT3')

pset$group <- factor(pset$group, levels = c('Low', 'High'))

res <- iobr_cor_plot(pdata_group           = pset,
                   id1                   = "ID",
                   feature_data          = eset_stad,
                   id2                   = "ID",
                   target                = NULL,
                   group                 = "group",
                   is_target_continuous  = FALSE,
                   padj_cutoff           = 1,
                   index                 = 2,
                   category              = "gene",
                   signature_group       = signature_collection[pos_sig],    
                   ProjectID             = 'NK',
                   palette_box           = "paired1",
                   palette_corplot       = "pheatmap",
                   palette_heatmap       = 4,
                   feature_limit         = 26,
                   character_limit       = 30,
                   show_heatmap_col_name = FALSE,
                   show_col              = FALSE,
                   show_plot             = TRUE,
                   path                  = paste0("2-relevant-genes"))

# wd <- '/Volumes/BiologyFish/Data/ZxProjects/COAD/20230824_CellDeathDis_MPLCs/01_preprocessing/50_IOBR'
# outdir <- file.path(wd, 'immune_IOBR')
# 
# write_xlsx(res, file.path(outdir, paste0('2_rel_genes.xlsx')))

```



# 6. GSEA scores between low and high groups
## 6.1 CD_8_T_effector expression between low and high groups
```{r}
boxplot <- sig_res_join %>% 
  select(ID, group, CD_8_T_effector)

summary(boxplot[boxplot$group=="Low",]$CD_8_T_effector)
summary(boxplot[boxplot$group=="High",]$CD_8_T_effector)

wilcox.test(boxplot[boxplot$group=="Low",]$CD_8_T_effector,boxplot[boxplot$group=="High",]$CD_8_T_effector)

```

```{r}
boxplot$group = factor(boxplot$group, levels=c('Low', 'High'))

pdf("20231114_TPM_CD_8_T_effector_boxplot_v1.pdf",height=5,width=5)
ggplot(boxplot,aes(x=group,y=CD_8_T_effector,color=factor(group)))+
  # geom_violin(width=0.45)+
  geom_boxplot(width=0.3)+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  #geom_quasirandom(width=0.1)+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.3, y=median(boxplot[boxplot$group=="Low",]$CD_8_T_effector), label=sprintf("%0.2f", median(boxplot[boxplot$group=="Low",]$CD_8_T_effector)), color = "#0000ff", size = 6)+
  annotate("text", x=2.3, y=median(boxplot[boxplot$group=="High",]$CD_8_T_effector), label=sprintf("%0.2f", median(boxplot[boxplot$group=="High",]$CD_8_T_effector)), color = "#dc143c", size = 6)+
  # scale_y_log10()+
  # ylim(0,6.5)+
  theme_classic()+theme(legend.position="NA")+
  # scale_fill_manual(values=c("#2ca9e1", "#e597b2"))+
  scale_color_manual(values=c("#0000ff", "#dc143c"))+
  labs(title = "CD_8_T_effector")+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+ylab(label = "Signature score")+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))
dev.off()

```

## 6.2 Immune_Checkpoint expression between low and high groups
```{r}
boxplot <- sig_res_join %>% 
  select(ID, group, Immune_Checkpoint)

summary(boxplot[boxplot$group=="Low",]$Immune_Checkpoint)
summary(boxplot[boxplot$group=="High",]$Immune_Checkpoint)

wilcox.test(boxplot[boxplot$group=="Low",]$Immune_Checkpoint,boxplot[boxplot$group=="High",]$Immune_Checkpoint)

```

```{r}
boxplot$group = factor(boxplot$group, levels=c('Low', 'High'))

pdf("20231114_TPM_Immune_Checkpoint_boxplot_v1.pdf",height=5,width=5)
ggplot(boxplot,aes(x=group,y=Immune_Checkpoint,color=factor(group)))+
  #geom_violin(width=0.45)+
  geom_boxplot(width=0.3)+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  #geom_quasirandom(width=0.1)+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.3, y=median(boxplot[boxplot$group=="Low",]$Immune_Checkpoint), label=sprintf("%0.2f", median(boxplot[boxplot$group=="Low",]$Immune_Checkpoint)), color = "#0000ff", size = 6)+
  annotate("text", x=2.3, y=median(boxplot[boxplot$group=="High",]$Immune_Checkpoint), label=sprintf("%0.2f", median(boxplot[boxplot$group=="High",]$Immune_Checkpoint)), color = "#dc143c", size = 6)+
  # scale_y_log10()+
  # ylim(0,6.5)+
  theme_classic()+theme(legend.position="NA")+
  # scale_fill_manual(values=c("#2ca9e1", "#e597b2"))+
  scale_color_manual(values=c("#0000ff", "#dc143c"))+
  labs(title = "Immune_Checkpoint")+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+ylab(label = "Signature score")+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))
dev.off()

```

## 6.3 Pan_F_TBRs expression between low and high groups
```{r}
boxplot <- sig_res_join %>% 
  select(ID, group, Pan_F_TBRs)

summary(boxplot[boxplot$group=="Low",]$Pan_F_TBRs)
summary(boxplot[boxplot$group=="High",]$Pan_F_TBRs)

wilcox.test(boxplot[boxplot$group=="Low",]$Pan_F_TBRs,boxplot[boxplot$group=="High",]$Pan_F_TBRs)

```

```{r}
boxplot$group = factor(boxplot$group, levels=c('Low', 'High'))

pdf("20231114_TPM_Pan_F_TBRs_boxplot_v1.pdf",height=5,width=5)
ggplot(boxplot,aes(x=group,y=Pan_F_TBRs,color=factor(group)))+
  #geom_violin(width=0.45)+
  geom_boxplot(width=0.3)+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  #geom_quasirandom(width=0.1)+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.3, y=median(boxplot[boxplot$group=="Low",]$Pan_F_TBRs), label=sprintf("%0.2f", median(boxplot[boxplot$group=="Low",]$Pan_F_TBRs)), color = "#0000ff", size = 6)+
  annotate("text", x=2.3, y=median(boxplot[boxplot$group=="High",]$Pan_F_TBRs), label=sprintf("%0.2f", median(boxplot[boxplot$group=="High",]$Pan_F_TBRs)), color = "#dc143c", size = 6)+
  # scale_y_log10()+
  # ylim(0,6.5)+
  theme_classic()+theme(legend.position="NA")+
  # scale_fill_manual(values=c("#2ca9e1", "#e597b2"))+
  scale_color_manual(values=c("#0000ff", "#dc143c"))+
  labs(title = "Pan_F_TBRs")+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+ylab(label = "Signature score")+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))
dev.off()

```

## 6.4 EMT1 expression between low and high groups
```{r}
boxplot <- sig_res_join %>% 
  select(ID, group, EMT1)

summary(boxplot[boxplot$group=="Low",]$EMT1)
summary(boxplot[boxplot$group=="High",]$EMT1)

wilcox.test(boxplot[boxplot$group=="Low",]$EMT1,boxplot[boxplot$group=="High",]$EMT1)

```

```{r}
boxplot$group = factor(boxplot$group, levels=c('Low', 'High'))

pdf("20231114_TPM_EMT1_boxplot_v1.pdf",height=5,width=5)
ggplot(boxplot,aes(x=group,y=EMT1,color=factor(group)))+
  #geom_violin(width=0.45)+
  geom_boxplot(width=0.3)+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  #geom_quasirandom(width=0.1)+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.3, y=median(boxplot[boxplot$group=="Low",]$EMT1), label=sprintf("%0.2f", median(boxplot[boxplot$group=="Low",]$EMT1)), color = "#0000ff", size = 6)+
  annotate("text", x=2.3, y=median(boxplot[boxplot$group=="High",]$EMT1), label=sprintf("%0.2f", median(boxplot[boxplot$group=="High",]$EMT1)), color = "#dc143c", size = 6)+
  # scale_y_log10()+
  # ylim(0,6.5)+
  theme_classic()+theme(legend.position="NA")+
  # scale_fill_manual(values=c("#2ca9e1", "#e597b2"))+
  scale_color_manual(values=c("#0000ff", "#dc143c"))+
  labs(title = "EMT1")+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+ylab(label = "Signature score")+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))
dev.off()

```

## 6.5 EMT2 expression between low and high groups
```{r}
boxplot <- sig_res_join %>% 
  select(ID, group, EMT2)

summary(boxplot[boxplot$group=="Low",]$EMT2)
summary(boxplot[boxplot$group=="High",]$EMT2)

wilcox.test(boxplot[boxplot$group=="Low",]$EMT2,boxplot[boxplot$group=="High",]$EMT2)

```

```{r}
boxplot$group = factor(boxplot$group, levels=c('Low', 'High'))

pdf("20231114_TPM_EMT2_boxplot_v1.pdf",height=5,width=5)
ggplot(boxplot,aes(x=group,y=EMT2,color=factor(group)))+
  #geom_violin(width=0.45)+
  geom_boxplot(width=0.3)+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  #geom_quasirandom(width=0.1)+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.3, y=median(boxplot[boxplot$group=="Low",]$EMT2), label=sprintf("%0.2f", median(boxplot[boxplot$group=="Low",]$EMT2)), color = "#0000ff", size = 6)+
  annotate("text", x=2.3, y=median(boxplot[boxplot$group=="High",]$EMT2), label=sprintf("%0.2f", median(boxplot[boxplot$group=="High",]$EMT2)), color = "#dc143c", size = 6)+
  # scale_y_log10()+
  # ylim(0,6.5)+
  theme_classic()+theme(legend.position="NA")+
  # scale_fill_manual(values=c("#2ca9e1", "#e597b2"))+
  scale_color_manual(values=c("#0000ff", "#dc143c"))+
  labs(title = "EMT2")+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+ylab(label = "Signature score")+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))
dev.off()

```

## 6.6 EMT3 expression between low and high groups
```{r}
boxplot <- sig_res_join %>% 
  select(ID, group, EMT3)

summary(boxplot[boxplot$group=="Low",]$EMT3)
summary(boxplot[boxplot$group=="High",]$EMT3)

wilcox.test(boxplot[boxplot$group=="Low",]$EMT3,boxplot[boxplot$group=="High",]$EMT3)

```

```{r}
boxplot$group = factor(boxplot$group, levels=c('Low', 'High'))

pdf("20231114_TPM_EMT3_boxplot_v1.pdf",height=5,width=5)
ggplot(boxplot,aes(x=group,y=EMT3,color=factor(group)))+
  #geom_violin(width=0.45)+
  geom_boxplot(width=0.3)+
  scale_y_continuous(expand = ggplot2::expansion(mult = c(0.1, 0.1)))+
  #geom_quasirandom(width=0.1)+
  geom_signif(comparisons = list(c("Low", "High")),
              map_signif_level=F,
              textsize=6,test=wilcox.test,step_increase=0.1,color="#000000")+
  annotate("text", x=1.3, y=median(boxplot[boxplot$group=="Low",]$EMT3), label=sprintf("%0.2f", median(boxplot[boxplot$group=="Low",]$EMT3)), color = "#0000ff", size = 6)+
  annotate("text", x=2.3, y=median(boxplot[boxplot$group=="High",]$EMT3), label=sprintf("%0.2f", median(boxplot[boxplot$group=="High",]$EMT3)), color = "#dc143c", size = 6)+
  # scale_y_log10()+
  # ylim(0,6.5)+
  theme_classic()+theme(legend.position="NA")+
  # scale_fill_manual(values=c("#2ca9e1", "#e597b2"))+
  scale_color_manual(values=c("#0000ff", "#dc143c"))+
  labs(title = "EMT3")+
  theme(panel.grid = element_blank(),axis.title = element_text(size = 15))+
  theme(plot.title = element_text(face="bold", color="black", size=20, hjust = 0.5))+
  xlab(label = NULL)+ylab(label = "Signature score")+
  theme(axis.line=element_line(size=0.5,colour="black"))+
  theme(axis.ticks=element_line(size=0.5,colour="black"),axis.ticks.length=unit(0.5,"lines"))+
  theme(axis.text.x = element_text(face="bold", color="black", size=15),
        axis.text.y = element_text(face="bold", color="black", size=15),
        axis.title.x = element_text(face="bold", color="black", size=15),
        axis.title.y = element_text(face="bold",color="black", size=15))
dev.off()

```

